Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-20 ApproximateCode.tex
till row 290

Unlike the RS code basing on additions and multiplications, another type of erasure codes is XOR-based codes and some are used in RAID (Redundant Arrays of Independent Drives) structures. This type of codes uses purely XOR operations, therefore showing a great advantage on encoding/decoding speed. XOR-based codes like EVENODD \cite{EVENODD} and H-code \cite{hcode} can tolerate 2 disk failures (EVENODD can even be designed to tolerate 3 disk failure), and they can be directly applied in RAID structures. More sophisticated ones like STAR code \cite{STAR} and TIP code \cite{tip} can tolerate 3 disk failures.

@@

First, the overhead of existing 3DFTs erasure codes is too high.
Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.

Based on these reasons, we propose a scheme for tiered video storage in a highly reliable environment, Approximate Code.
Approximate code is an erasure code framework that uses tiered storage\cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot} and approximate storage strategies to separate an existing erasure codes into codes with different fault tolerances and apply them to important and unimportant data.

@@

Since \emph{Structure I} distributes important data across each node, it guarantees a more balanced load. \emph{Structure II} concentrates important data into an array, and provides greater reliability for important data. A detailed analysis of this will be presented in \ref{evaluation}.

@@

In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
Approximate Code are designed for $h$ arrays, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks, so the total number of nodes in Approximate Code ($k,r,g,h$) is 
$h*(k+r) + g$.

@@

As introduced in \ref{existEC}, STAR Code \cite{huang2008star} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
%We usually split the XOR-based code into a horizontal parity (local) and (anti-)diagonal parities (global), whereas the STAR feature allows it to support another segmentation method.
Since STAR is a direct extension of EVENODD\cite{blaum1995evenodd}, that is to say, the STAR that removes the anti-diagonal parity is the typical RAID-6 code EVENODD. As shown in Figure \ref{fig-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
According to the construction requirements of STAR, each node is divided into 4 blocks.

@@

Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure I}, based on RAID5 and TIP-code \cite{zhang2015tip}. RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code. In each array, local parity blocks provide horizontal XOR parity, and between arrays, global parity provide diagonal parity and anti-diagonal parity.

>>>>

Unlike the RS code basing on additions and multiplications, another type of erasure codes is XOR-based codes and some are used in RAID (Redundant Arrays of Independent Drives) structures. This type of codes uses purely XOR operations, therefore showing a great advantage on encoding/decoding speed. Typical XOR-based MDS codes are EVENODD code \cite{EVENODD}, H-code \cite{hcode}, STAR code \cite{STAR} and TIP-code \cite{tip}. Some of them will be discussed in detail below.

@@

First, the overhead of existing 3DFTs erasure codes is too high.
Secondly, the 2DFTs erasure codes sacrifice part of the necessary reliability, and that of approximate storage schemes is much lower since they cannot tolerate disk-level failures.
Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.

Based on these reasons, we propose a scheme for tiered video storage in a highly reliable environment, named Approximate Code.
Approximate code is an erasure code framework that uses tiered storage\cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot} and approximate storage strategies to separate an existing erasure codes into codes with different fault tolerances and apply them to important and unimportant data.

@@

Since \emph{Structure I} distributes important data across each node, it guarantees a more balanced load. \emph{Structure II} aggregates important data into an array, and provides greater reliability for important data. A detailed analysis of this will be presented in \ref{evaluation}.

@@

In an $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
Approximate Code are designed for $h$ arrays, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks, so the total number of nodes in Approximate Code ($k,r,g,h$) is 
$h*(k+r) + g$.

@@

As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
%We usually split the XOR-based code into a horizontal parity (local) and (anti-)diagonal parities (global), whereas the STAR feature allows it to support another segmentation method.
Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, the STAR that removes the anti-diagonal parity is the typical RAID-6 code EVENODD. As shown in Figure \ref{fig-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
According to the construction requirements of STAR, each node is divided into 4 blocks.

@@

Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure I}, based on RAID5 and TIP-code \cite{tip}. RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code. In each array, local parity blocks provide horizontal XOR parity, and between arrays, global parity provide diagonal parity and anti-diagonal parity.
